A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-19 manuscript.Rmd
cache screenshot of readme

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  vwidth = 1920, # height & width are not resolution
                  vheight = 1080, # but what website thinks the browser size is
                  selector = "div#readme",
                  zoom = 2) # higher resolution
```

>>>>

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
if (!file.exists(readme)) {
  webshot2::webshot(
    "https://github.com/aaronpeikert/repro-tutorial/",
    file = readme,
    vwidth = 1920,
    # height & width are not resolution
    vheight = 1080,
    # but what website thinks the browser size is
    selector = "div#readme",
    zoom = 2
  ) # higher resolution
}
```
